---
title: "Yemen Data Project 2019"
output: html_notebook
---

Import libraries and dataset from the Yemen data project
```{r}
library(plyr)
library(tidyverse)
library(jsonlite)
library(lubridate)
full_dataset <- read_csv("YDP.csv")
calendar <- read_csv("calendar.csv")
head(full_dataset)
head(calendar)
```

Select and rename the columns that we want
```{r}
dataset <- full_dataset %>% select(`Incident ID`,Date,Governorate,`Air Strikes Min.`,`Air Strikes Max.`) %>% rename(ID=`Incident ID`, Gov=Governorate, Raid=`Air Strikes Min.`,Max=`Air Strikes Max.`)  %>% mutate(Date=dmy(Date))
```

Remove all (+) values and inject integers
```{r}
MaxClean <- str_replace_all(dataset$Max, "\\+", "")
Max1 <- as.integer(MaxClean)
dataset$Max <- Max1
head(dataset)
```

Calculate the number of raids irrespective of the number of strikes
```{r}
dtotal <- dataset %>% group_by(Date) %>% summarize(Total = sum(Raid))
#This calculated the number of strikes as the sum of raids
#dtotal <- dataset %>% group_by(Date) %>% summarize(Total = sum(Max))
head(dtotal$Total)


```

Group by date for each Governorate and calculate the total nuber of raids. (Replace sum(Raid) with sum(Max) to calculate number of strikes)
```{r}
dSaada <- dataset %>% group_by(Date) %>% filter(Gov=="Saada") %>% summarize (Saada = sum(Raid))
dTaiz <- dataset %>% group_by(Date) %>% filter(Gov=="Taiz") %>% summarize (Taiz = sum(Raid))
dSanaa <- dataset %>% group_by(Date) %>% filter(Gov=="Sanaa") %>% summarize (Sanaa = sum(Raid))
dHajja <- dataset %>% group_by(Date) %>% filter(Gov=="Hajja") %>% summarize (Hajja = sum(Raid))
dHudaydah <- dataset %>% group_by(Date) %>% filter(Gov=="Hudaydah") %>% summarize (Hodeidah = sum(Raid))
dMarib <- dataset %>% group_by(Date) %>% filter(Gov=="Marib") %>% summarize (Marib = sum(Raid))
dAmanatalAsimah <- dataset %>% group_by(Date) %>% filter(Gov=="Amanat al Asimah") %>% summarize (`Amanat al Asimah` = sum(Raid))
dJawf <- dataset %>% group_by(Date) %>% filter(Gov=="Jawf") %>% summarize (Jawf = sum(Raid))
dBayda <- dataset %>% group_by(Date) %>% filter(Gov=="Bayda") %>% summarize (Bayda = sum(Raid))
dLahj <- dataset %>% group_by(Date) %>% filter(Gov=="Lahj") %>% summarize (Lahj = sum(Raid))
dAmran <- dataset %>% group_by(Date) %>% filter(Gov=="Amran") %>% summarize (Amran = sum(Raid))
dShabwa <- dataset %>% group_by(Date) %>% filter(Gov=="Shabwa") %>% summarize (Shabwa = sum(Raid))
dAden <- dataset %>% group_by(Date) %>% filter(Gov=="Aden") %>% summarize (Aden = sum(Raid))
dIbb <- dataset %>% group_by(Date) %>% filter(Gov=="Ibb") %>% summarize (Ibb = sum(Raid))
dDhamar <- dataset %>% group_by(Date) %>% filter(Gov=="Dhamar") %>% summarize (Dhamar = sum(Raid))
dDhalie <- dataset %>% group_by(Date) %>% filter(Gov=="Dhalie") %>% summarize (Dhalie = sum(Raid))
dAbyan <- dataset %>% group_by(Date) %>% filter(Gov=="Abyan") %>% summarize (Abyan = sum(Raid))
dMahwit <- dataset %>% group_by(Date) %>% filter(Gov=="Mahwit") %>% summarize (Mahwit = sum(Raid))
dRaymah <- dataset %>% group_by(Date) %>% filter(Gov=="Raymah") %>% summarize (Raymah = sum(Raid))
dHadramawt <- dataset %>% group_by(Date) %>% filter(Gov=="Hadramawt") %>% summarize (Hadramawt = sum(Raid))
```

Combine all the tables
```{r}
combined_dataset<-join_all(list(dtotal,dSaada,dTaiz,dSanaa,dHajja,dHudaydah,dMarib,dAmanatalAsimah,dJawf,dBayda,dLahj,dAmran,dShabwa,dAden,dIbb,dDhamar,dDhalie,dAbyan,dMahwit,dRaymah,dHadramawt), by='Date', type='left')

combined_alldates <- join_all (list(calendar,combined_dataset), by="Date", type="left")

#to replace missing values with zero
allcalendardata <- combined_alldates %>% replace(is.na(.), 0)

head(allcalendardata[63:68,])

combined_dataset_rev <- combined_alldates %>% map_df(rev)
head(combined_dataset_rev)
```

Add the Audio classification
```{r}
catfunction <- function(x) {
    if(x==0){
	dcategory = "file '0,mp3'"
}else if (x <= 5 & x > 0){
	dcategory = "file '1.mp3'"
}else if (x <= 10 & x > 5){
	dcategory = "file '2.mp3'"
}else if (x <= 15 & x > 10){
	dcategory = "file '3.mp3'"
}else if (x <= 20 & x > 15){
	dcategory = "file '4.mp3'"
}else if (x <= 25 & x > 20){
	dcategory = "file '5.mp3'"
}else if (x <= 30 & x > 25){
	dcategory = "file '6.mp3'"
}else if (x <= 35 & x > 30){
	dcategory = "file '7.mp3'"
}else if (x <= 40 & x > 35){
	dcategory = "file '8.mp3'"
}else if (x <= 45 & x > 40){
	dcategory = "file '9.mp3'"
}else if (x <= 50 & x > 45){
	dcategory = "file '10.mp3'"
}else if (x <= 55 & x > 50){
	dcategory = "file '11.mp3'"
}else if (x <= 60 & x > 55){
	dcategory = "file '12.mp3'"
}else{
	dcategory = "file '13.mp3'"
}
}
AudioCategory <- unlist(lapply(allcalendardata$Total,catfunction))
AudioCategory<-as.data.frame(AudioCategory)

write_csv(AudioCategory, "AudioCat.csv")
```

Export the calendar data
```{r}
calendardata <- combined_alldates %>% select(Date,Total) %>% rename(day=Date, value=Total)
toJSON(calendardata)
write_json(calendardata, "YemenCalendar.json")
write_csv(calendardata, "YemenCalendar.csv", na = "0")
```

Export data as JSON
```{r}

toJSON(combined_alldates)
toJSON(combined_dataset_rev)
write_json(combined_alldates, "YemenData.json")
write_json(combined_dataset_rev, "YemenDataRev.json")
write_csv(combined_alldates, "rprocessed.csv", na = "0")
write_csv(combined_dataset_rev, "rprocessedRev.csv", na = "0")

```
